\vspace{\baselineskip} The population of long-period transiting exoplanets \vspace{-2\baselineskip}

### 2016-09-29 document/ms.tex
comments about geometry

\response{%
In \eq{geom-comp}, the term $(R_{\star,k}+R)$ takes grazing transits into
account.
This might seem counter intuitive because, as part of the search procedure, we
rejected candidates where the maximum likelihood model had a grazing transit.
However, since the measurement of $Q_{\mathrm{det},k}$ included a cut on the
measured impact parameter, we argue that the $Q_{\mathrm{det},k}$ already
takes this effect into account.
In other words, $Q_{\mathrm{det},k}$ quantifies the probability that a transit
of a given shape will be detected \emph{given that it transits at all} and
$Q_{\mathrm{geom},k}$~--~the way it is written in \eq{geom-comp}~--~is the
marginalized probability that the system will transit given its physical
parameters.
}

@@

% \acknowledgments
\vspace{1.5em}
It is a pleasure to thank
Jeff Coughlin,
So Hattori,
Heather Knutson,
Hans-Walter Rix,
Dun Wang,
and
Angie Wolfgang
for helpful discussions and contributions.

>>>>

\response{%
In \eq{geom-comp}, the term $(R_{\star,k}+R)$ takes grazing transits into
account.
This might seem counter intuitive because, as part of the search procedure, we
rejected candidates where the maximum likelihood model had a grazing transit.
However, since the measurement of $Q_{\mathrm{det},k}$ included a cut on the
measured impact parameter, the $Q_{\mathrm{det},k}$ term already takes this
effect into account.
In other words, $Q_{\mathrm{det},k}$ quantifies the probability that a transit
of a given shape will be detected \emph{given that it transits at all} and
$Q_{\mathrm{geom},k}$~--~the way it is written in \eq{geom-comp}~--~is the
marginalized probability that the system will transit given its physical
parameters.
}

@@

% \acknowledgments
\vspace{1.5em}
It is a pleasure to thank
Jeff Coughlin,
So Hattori,
Heather Knutson,
Phil Muirhead,
Darin Ragozzine,
Hans-Walter Rix,
Dun Wang,
and
Angie Wolfgang
for helpful discussions and contributions.
